#Reproducible Research - Course Project 1

### 1. R code to read the downloaded dataset - Activity monitoring data.

```{r, echo=TRUE}
activity <- read.csv("activity.csv")
sapply(activity, class)
summary(activity)
```

### 2. Tranform the data in a suitable format

```{r, echo=TRUE}
activity$date <- as.Date(activity$date, format = "%Y-%m-%d")
suppressWarnings(library(zoo))
```

### 3. Make a histogram of the total number of steps taken each day.

```{r, echo=TRUE}
colMeans(is.na(activity))
steps_day <- aggregate(steps ~ date, rm.na = TRUE, data = activity, FUN = sum)

plot(steps_day, type = "h", lwd = 10, lend = "square")
```

### 4. Mean and median number of steps taken each day

```{r, echo=TRUE}
aggregate(steps ~ date, data = activity, FUN = mean)
aggregate(steps ~ date, data = activity, FUN = median)
```

### 5. To calculate average daily activity pattern.

#### 5.1  Make a time series plot (i.e. type = “l”) of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=TRUE}
plot(aggregate(steps ~ interval, data = activity, FUN = mean),type = "l")
```

#### 5.2 Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}
max(activity$steps, na.rm = TRUE)
```

